A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise ZBDDs

This representation is especially useful when the data can be represented as
(sparse) bit vectors. Any subset of these bit vectors can be represented by a
Boolean function over $n$ variables. If the corresponding bit vector is in the
set, the \textit{Zero-Suppressed BDDs} (\textit{ZBDDs}) yields 1 for a given
variable assignment.

The bit vector are \textit{sparse} in the sense that the set contains much less
than $2^n$ vectors and the bit vectors themselves have many zero elements. ZBDDs
are similar to OBDDs but they use a different reduction rule, exploiting the
sparse bit vectors. In ZBDDs, nodes can be eliminated whenever setting the
corresponding variable to 1 yields 0 as result, which is often the case for sparse
bit vectors. This representation proved successful to solve some combinatorial
problems~\cite{BRYANT95}. \tbr %\newpage

@@

Analogous to OBDDs and FDDs, OBEDs and FBEDs can be defined, whereas OBEDs are
OBDDs without operator nodes. The reduction rule of BEDs is similar to the one
of OBDDs but extended with an additional rule for operator nodes. For any operator
nodes $n$ it has to hold that $lo(n)$ and $hi(n)$ are nonterminals in order to
guarantee reducedness. Apart from that, before generating a new node, an existence
check is performed. If there exists an equivalent node, this node is reused.
Otherwise the new node is created and considered in the next check. However, even
if a BED is reduced, canonicity is not guaranteed (in contrast to
OBDDs)~\cite{ANDERSEN97}.

>>>>

This representation is especially useful when the data can be represented as
(sparse) bit vectors. Any subset of these bit vectors can be represented by a
Boolean function over $n$ variables. If the corresponding bit vector is in the
set, the \textit{Zero-Suppressed BDD} (\textit{ZBDD}) yields 1 for a given
variable assignment.

Bit vectors are \textit{sparse} in the sense that the set of bit vectors contains
much less than all possible $2^n$ bit vectors and the bit vectors themselves
contain many zero elements. ZBDDs are similar to OBDDs but they use a different
reduction rule, exploiting the sparseness of the bit vectors. In ZBDDs, nodes can be
eliminated whenever setting the corresponding variable to 1 yields 0 as result,
which is often the case for sparse bit vectors. This representation proved
successful to solve some combinatorial problems~\cite{BRYANT95}.

@@

Analogous to OBDDs and FBDDs, OBEDs and FBEDs can be defined, whereas OBEDs are
OBDDs without operator nodes. The reduction rule of BEDs is similar to the one
of OBDDs but extended with an additional rule for operator nodes. For any operator
nodes $n$ it has to hold that $lo(n)$ and $hi(n)$ are nonterminals in order to
guarantee reducedness. Apart from that, before generating a new node, an existence
check is performed. If there exists an equivalent node, this node is reused.
Otherwise the new node is created and considered in the next check. However, even
if a BED is reduced, canonicity is not guaranteed (in contrast to
OBDDs)~\cite{ANDERSEN97}.
